Classless Java

### 2016-03-24 OOPSLA16/paper.tex
abstract fix

  This paper introduces \interfacebased (IB) \objectoriented (OO)
  programming. Unlike \classbased OO programming, in IB programming there
  is no need for classes. To support state, IB programming does not
  use fields directly. Instead it uses \emph{abstract state
    operations}, such as getters, setters or clone-like methods. This
  new way to deal with state allows flexibility not typically
  available in CB languages.  In IB state (including mutable state)
  can be type-refined in subtypes. The combination of a
  purely IB style of programming and type-refinement enables
  powerful idioms using multiple inheritance and state.  To introduce
  IB to programmers we created Classless Java: an embeding of IB
  directly into Java. Classless Java uses annotation processing for
  code generation, and relies on new features of Java 8 for
  interfaces. We illustrate the usefulness of IB through various
  examples and case studies.

>>>>

  This paper introduces \interfacebased \objectoriented 
  programming (in short IB). Unlike class based OO programming, in IB there
  is no need for classes. To support state, IB does not
  use fields directly. Instead it uses \emph{abstract state
    operations}, such as getters, setters or clone-like methods. This
  new way to deal with state allows flexibility not typically
  available in CB languages.  In IB state (including mutable state)
  can be type-refined in subtypes. The combination of a
  purely IB style of programming and type-refinement enables
  powerful idioms using multiple inheritance and state.  To introduce
  IB to programmers we created Classless Java: an embeding of IB
  directly into Java. Classless Java uses annotation processing for
  code generation, and relies on new features of Java 8 for
  interfaces. We illustrate the usefulness of IB through various
  examples and case studies.
